COCT Urban Mobility

### 2023-08-12 draft_v0_1.Rmd
Comparisons add, pre-dashboard mock-up. From Windows.

---
title: "Untitled"
output: html_document
date: "2023-08-11"
editor_options: 
  chunk_output_type: console
---

@@

Describe brief, outline of document.

@@

@@

@@

tmp <- dta %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  inner_join(dta %>% 
  filter(is.na(directorate) & !is.na(official_suburb)) %>% 
  group_by(official_suburb) %>% 
  count(name = "n_missing")) %>% 
  mutate(percentage_missing = n_missing/total_suburb*100) %>% 
  filter(n_missing >= n_cutoff) %>% 
  arrange(desc(percentage_missing), desc(n_missing)) %>% 
  ungroup()

@@

tmp <- dta %>% 
  select(directorate, department, branch, section, official_suburb) %>% 
  mutate(across(everything(), ~as.numeric(is.na(.x)))) %>% 
  as.data.frame()
head(tmp)

@@

Missingness of specific data entries can be meaningful, e.g. it can point to operational failures if a specific region has more missing data than another.  Therefore it is important to interrogate patterns of missingness in data. We investigated missingness that would make interpretation hard.  Entries for which any of the Directorate, Department, Branch, Section or Official suburb were missing are visualised (Figure A). Entries with missing Directorate were in general also missing for the other categories. Suburbs for which there were at least `r n_cutoff` entries, and for which Directorate was missing, but Official suburb was not(n = `r mis_dir_nonmis_sub`), accounted for at most `r tmp$percentage_missing` of entries for any suburb and the suburb with the highest percentage of missing entries of this kind, was `r tmp$official_suburb[tmp$percentage_missing == max(tmp$percentage_missing)]`(Figure B).

@@

plotdta <- dta %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  inner_join(dta %>% 
  filter(is.na(directorate) & !is.na(official_suburb)) %>% 
  group_by(official_suburb) %>% 
  count(name = "n_missing")) %>% 
  mutate(percentage_missing = n_missing/total_suburb*100) %>% 
  arrange(desc(n_missing), desc(percentage_missing)) %>% 
  ungroup()

@@

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, is.na(directorate)) %>% 
               count(name = "n_missing")) %>%
  ungroup() %>% 
  rename(missing_directorate = 4) %>% 
  filter(missing_directorate == TRUE) %>% 
  mutate(percentage_missing = n_missing/total_ym*100) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

@@

# Missingness in urban mobility
unique(dta$directorate)

dta_um <- dta %>% 
  filter(directorate == "URBAN MOBILITY")

x <- which(names(dta_um) %in% c("code_group", "code", "cause_code_group", "cause_code"))

map(dta_um[x], ~sort(unique(.x))) 
map(dta_um[x], ~sum(is.na(.x)))

dta_um %>%
  select(all_of(x)) %>% 
  group_by(is.na(.)) %>% 
  count()

x <- nrow(dta_um)

x1 <- dta_um %>% 
  group_by(is.na(cause_code_group), is.na(cause_code)) %>% 
  count(name = "missing_cause") %>% 
  ungroup() %>% 
  rename(...1 = 1, ...2 = 2) %>% 
  filter(...1 == TRUE & ...2 == TRUE) %>% 
  pull(missing_cause)

tibble(msg = glue::glue("Missing cause for {round(x1/x*100, 2)}% of Urban Mobility entries.")) %>% 
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE, position = "left")

@@

### Description of the data and preparation steps

@@

dta %>% 
  group_by(directorate) %>% 
  count(name = "Nr_of_entries") %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/x*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  rename(Directorate = directorate) %>% 
  kable(title = "Number and percentage of entries per Directorate") %>%
  kable_styling(full_width = FALSE, position = "left")

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, directorate) %>% 
               count(name = "Nr_of_entries")) %>% 
  ungroup() %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/total_ym*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  ggplot(aes(month_creation, Percentage_of_total, 
             fill = reorder(directorate, Percentage_of_total)))+
  geom_col()+
  facet_wrap(~year_creation, scales = "free_x") # resize left bar?

@@

@@

```{r}
# department, branch, section, code_group not helpful
dta_um %>% 
  group_by(code, cause_code) %>% 
  count() %>% 
  print(n = Inf)

# filter out cause codes "Not Defined" etc, but keep NA

dta_um <- dta_um %>% 
  filter(!cause_code %in% c("No Cause Found",
                           "None/Private") &
           !is.na(official_suburb))

dta_um %>% 
  group_by(official_suburb) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  print(n = 20)

# top 10 by month

plotdta <- dta_um %>% 
  group_by(year_creation, month_creation, official_suburb) %>% 
  count() %>% 
  arrange(year_creation, month_creation, desc(n)) %>% 
  print(n = 20) %>% 
  ungroup()

plotdta <- map(unique(plotdta$month_creation),
           ~plotdta %>% 
  filter(month_creation == .x) %>% 
  arrange(desc(n)) %>% 
  slice(1:10)) %>% 
    bind_rows()

dta_um %>% 
  group_by(official_suburb) %>% 
  count(name = "total_overall") %>% 
  inner_join(plotdta) %>% 
  ggplot(aes(n, official_suburb, fill = total_overall))+
  geom_col()+
  facet_wrap(~month_creation)

# looks like parklands, milnerton, table view, marconi beam

# if look at median across months
dta_um %>% 
  group_by(month_creation, official_suburb) %>% 
  count() %>% 
  ungroup() %>% 
  group_by(official_suburb) %>% 
  summarise(med = median(n)) %>% 
  ungroup() %>% 
  arrange(desc(med))

x <- c("PARKLANDS", "MARCONI BEAM", "BRACKENFELL COMMON",
       "TABLE VIEW", "MILNERTON")

dta_um %>% 
  filter(official_suburb %in% x) %>% 
  group_by(official_suburb, code) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(aes(n, code, fill = official_suburb))+
  geom_col(position = "dodge")

@@

```{r}
# get back no fault found etc.

dta_um <- dta %>% 
  filter(directorate == "URBAN MOBILITY")

# completion time missing
x <- nrow(dta_um)

dta_um %>% 
  group_by(is.na(completion_timestamp)) %>% 
  count(name = "Nr") %>% 
  ungroup() %>% 
  rename(Missing_completion_time = 1) %>% 
  mutate(across(Missing_completion_time, ~ifelse(.x == TRUE, "yes", "no")),
         Percentage = round(Nr/x*100, 2)) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

# breakdown of entries with missing completion times

x <- c("department", "branch", "section", "code_group",
  "code", "cause_code_group", "cause_code", "official_suburb")

tmp <- map(x, 
    ~dta_um %>% 
  filter(is.na(completion_timestamp)) %>% 
  select(notification_number, all_of(.x)) %>% 
  mutate(across(-notification_number, ~paste(cur_column(), .x, sep = ":")),
         value = 1) %>% 
    rename(key = 2) %>% 
  pivot_wider(names_from = key, values_from = value)) %>% 
  purrr::reduce(inner_join) %>% 
  as.data.frame()

tmp[is.na(tmp)] <- 0

UpSetR::upset(tmp)

@@

dta_um <- dta_um %>% 
  filter(!is.na(completion_timestamp)) %>% 
   mutate(time_hrs = as.integer(completion_timestamp - creation_timestamp)/60)

@@

```{r}
#  create table withs medians, q80 for all suburbs and for all of city

time_tables_make <- function(dataset = dta_um, time_cutoff = NULL){

@@

  tabledta <- dataset %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
                 mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

  dataset_x <- dataset %>% 
    filter(time_hrs < time_cutoff)

  tabledta_below <- dataset_x %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

  dataset_x <- dataset %>% 
    filter(time_hrs >= time_cutoff)

  tabledta_above <- dataset_x %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(med_time_hrs = median(time_hrs),
            q80_time_hrs = quantile(time_hrs, probs = 0.8)) %>% 
    ungroup())

@@

time_dta_list$all_times <- time_tables_make(dataset = dta_um, time_cutoff = NULL)

# for all of city, all codes, split by times < or > 96hrs
tmp <- time_tables_make(dataset = dta_um, time_cutoff = 96)

time_dta_list$below_96 <- tmp$tabledta_below 
time_dta_list$above_eq_96 <- tmp$tabledta_above

@@

time_dta_list$all_times %>% 
  filter(official_suburb == sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  kable(caption = "City-wide, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hrs)) %>% 
  slice(1:5) %>% 
  kable(caption = "Top 5 suburbs with long median completion times, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(med_time_hrs) %>% 
  slice(1:5) %>% 
  kable(caption = "Top 5 suburbs with short median completion times, all codes combined") %>%
  kable_styling(full_width = FALSE, position = "left")

@@

tmp <- time_dta_list$all_times %>% 
  filter(official_suburb == sub_txt &
           code != code_txt &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hrs))

code_txt <- tmp$code[2]

plotdta <- tmp %>% 
  mutate(set = "City-wide") %>% 
  filter(code == code_txt) %>% 
  bind_rows(time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n != 1) %>% 
  arrange(desc(med_time_hrs)) %>% 
  slice(1:5) %>% 
    mutate(set = "top_long_times")) %>% 
  bind_rows(time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt,
         n != 1) %>% 
  arrange(med_time_hrs) %>% 
  slice(1:5) %>% 
    mutate(set = "top_short_times")) %>% 
  pivot_longer(cols = c(med_time_hrs, q80_time_hrs),
               names_to = "quantile", values_to = "time_hrs")

x <- plotdta %>% 
  filter(quantile == "med_time_hrs") %>% 
  select(official_suburb, time_hrs) %>% 
  arrange(desc(time_hrs)) %>% 
  pull(official_suburb)

plotdta$official_suburb <- factor(plotdta$official_suburb,
                                  levels = unique(x))

plotdta %>% 
  ggplot(aes(time_hrs, official_suburb, colour = set))+
  geom_point()

@@

plotdta <- dta_um %>% 
  mutate(diff_time_hrs = as.integer(completion_timestamp - creation_timestamp)/60) %>% 
  select(notification_number, diff_time_hrs, code_group, code, cause_code_group,
         cause_code, official_suburb)

plot_time_per_var <- function(dataset = plotdta, column = "code_group", hours_cutoff = 96){

  x <- which(names(dataset) == column)
  dataset <- dataset %>% 
    rename(col_select = x)

  tmp <- dataset %>% 
  group_by(col_select) %>% 
  summarise(n = n(),
            med_hrs = median(diff_time_hrs),
            q5 = quantile(diff_time_hrs, probs = 0.05),
            q80 = quantile(diff_time_hrs, probs = 0.8),
            q95 = quantile(diff_time_hrs, probs = 0.95)) %>% 
  ungroup()

  dataset %>% 
    mutate(col_select = "all_combined") %>% 
    group_by(col_select) %>% 
  summarise(n = n(),
            med_hrs = median(diff_time_hrs),
            q5 = quantile(diff_time_hrs, probs = 0.05),
            q80 = quantile(diff_time_hrs, probs = 0.8),
            q95 = quantile(diff_time_hrs, probs = 0.95)) %>% 
  ungroup()

p1 <- tmp %>% 
  filter(q95 < hours_cutoff) %>% 
  select(col_select) %>% 
  inner_join(dataset %>% 
               select(col_select, diff_time_hrs)) %>% 
  ggplot(aes(diff_time_hrs, col_select))+
  ggdist::stat_interval()+
  labs(y = column)

p2 <- tmp %>% 
  filter(q5 >= hours_cutoff) %>% 
  select(col_select) %>% 
  inner_join(dataset) %>% 
  mutate(time_weeks = (diff_time_hrs/24)/7) %>% 
  ggplot(aes(time_weeks, col_select))+
  ggdist::stat_interval()+
  labs(y = column)

return(list(hours = p1, weeks = p2))

plotlist <- plot_time_per_var(dataset = plotdta, column = "code_group", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "code", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "cause_code_group", hours_cutoff = 96)

ggpubr::ggarrange(plotlist = plotlist)

plotlist <- plot_time_per_var(dataset = plotdta, column = "cause_code", hours_cutoff = 96)

>>>>

---
title: "COCT Urban Mobility"
output: pdf_document
author:  "E Maasdorp"
date: "`r format(Sys.time(), '%d %B %Y')`"
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}
    \includegraphics[width=2in,height=2in]{img/city_emblem.png}\LARGE\\}
  - \posttitle{\end{center}}
editor_options: 
  chunk_output_type: console
---

@@

**Note from the author:  This report was compiled to complete the City of Cape Town (COCT) data science challenge.  It is not an official COCT report.**  
The goal of this analysis was to highlight COCT suburbs that the Urban Mobility Directorate should focus on, for infrastructure improvements, based on service request data for 4 months (December 2020 to March 2021). It also explored intervals between creation and completion of service requests, to identify performance across the city. Finally, a suggested performance tracking dashboard is provided, and insights are provided to aid

@@

coct_cols <- c("#C7006E", "#B9CF00","#00A6CD", "#FF9900",  "#000000")

theme_set(theme_light())

@@

# parameters

select_directorate <- "URBAN MOBILITY"
# specify the Directorate this analysis focuses on

@@

tmp1 <- dta %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  inner_join(dta %>% 
  filter(is.na(directorate) & !is.na(official_suburb)) %>% 
  group_by(official_suburb) %>% 
  count(name = "n_missing")) %>% 
  mutate(percentage_missing = n_missing/total_suburb*100) %>% 
  filter(n_missing >= n_cutoff) %>% 
  arrange(desc(percentage_missing), desc(n_missing)) %>% 
  ungroup()

@@

tmp <- dta %>% 
  select(directorate, department, branch, section, official_suburb) %>% 
  mutate(across(everything(), ~as.numeric(is.na(.x)))) %>% 
  as.data.frame()

@@

Missingness of specific data entries can be meaningful, e.g. it can point to operational failures if a specific region has more missing data than another.  Therefore it is important to interrogate patterns of missingness in data. We investigated missingness that would make interpretation hard.  Entries for which any of the Directorate, Department, Branch, Section or Official suburb were missing are visualised (Figure A). Entries with missing Directorate were in general also missing for the other categories. Suburbs for which there were at least `r n_cutoff` entries, and for which Directorate was missing, but Official suburb was not(n = `r mis_dir_nonmis_sub`), accounted for at most `r max(tmp1$percentage_missing)` of entries for any suburb and the suburb with the highest percentage of missing entries of this kind, was `r tmp1$official_suburb[tmp1$percentage_missing == max(tmp1$percentage_missing)]`(Figure B).

@@

n_cutoff <- 5
plotdta <- dta %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  inner_join(dta %>% 
  filter(is.na(directorate) & !is.na(official_suburb)) %>% 
  group_by(official_suburb) %>% 
  count(name = "n_missing")) %>% 
  mutate(percentage_missing = n_missing/total_suburb*100) %>% 
  filter(n_missing >= n_cutoff) %>% 
  arrange(desc(percentage_missing)) %>% 
  ungroup()

@@

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, is.na(directorate)) %>% 
               count(name = "n_missing")) %>%
  ungroup() %>% 
  rename(missing_directorate = 4) %>% 
  filter(missing_directorate == TRUE) %>% 
  mutate(percentage_missing = n_missing/total_ym*100) %>% 
  kable(format = "simple") %>%
   kable_styling(position = "left")

@@

Missingness in specific directorate

# Missingness in specific directorate

dta_dir <- dta %>% 
  filter(directorate == select_directorate)

x <- which(names(dta_dir) %in% c("code_group", "code", "cause_code_group", "cause_code"))

# map(dta_dir[x], ~sort(unique(.x))) 
# map(dta_dir[x], ~sum(is.na(.x))) 
# 
# dta_dir %>%
#   select(all_of(x)) %>% 
#   group_by(is.na(.)) %>% 
#   count()

x <- nrow(dta_dir)

x1 <- dta_dir %>% 
  group_by(mis_code_grp = is.na(cause_code_group), 
           mis_cause_code = is.na(cause_code)) %>% 
  count(name = "missing_cause") %>% 
  ungroup() %>% 
  filter(mis_code_grp == TRUE & mis_cause_code == TRUE) %>% 
  pull(missing_cause)

# tibble(msg = glue::glue("Missing cause for {round(x1/x*100, 2)}% of {select_directorate} entries.")) %>% 
#   kable(col.names = NULL) %>%
#   kable_styling(full_width = FALSE, position = "left")

Missing completion dates for `r select_directorate`.

dta_dir %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            missing_completion_time = 
              sum(is.na(completion_timestamp))) %>% 
  filter(missing_completion_time != 0) %>% 
  kable(format = "simple") %>%
  kable_styling(position = "left")

@@

## Overview of all Directorates

Contextualise

@@

tmp <- dta %>% 
  group_by(directorate) %>% 
  count(name = "Nr_of_entries") %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/x*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  rename(Directorate = directorate)

x <- which(tmp$Directorate == select_directorate)

tmp %>% 
  kable(format = "simple", caption = "Number and percentage of entries per Directorate") %>%
  kable_styling( position = "left") %>% 
  row_spec(row = x, bold = TRUE)

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, directorate) %>% 
               count(name = "Nr_of_entries")) %>% 
  ungroup() %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/total_ym*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  ggplot(aes(month_creation, Percentage_of_total, 
             fill = reorder(directorate, Percentage_of_total)))+
  geom_col()+
  facet_wrap(~year_creation, scales = "free_x")

tmp <- dta %>% 
  filter(!is.na(official_suburb)) %>% 
  group_by(directorate) %>% 
  count(name = "total_directorate") %>% 
  inner_join(dta %>% 
               filter(!is.na(official_suburb)) %>% 
               group_by(directorate, official_suburb) %>% 
               count(name = "total_suburb")) %>% 
  mutate(percentage = total_suburb/total_directorate*100)

map(unique(tmp$directorate),
    ~tmp %>% 
      filter(directorate == .x) %>% 
      arrange(desc(percentage)) %>% 
      slice(1:3)) %>% 
  bind_rows() %>% 
  ggplot(aes(percentage, official_suburb, fill = directorate))+
  geom_col()+
  facet_wrap(~directorate, scales = "free_y",
             nrow = 2)+
  theme(legend.position = "none")

@@

## Focused Analysis: Directorate `r select_directorate`

@@

# Number of requests over time, including missing suburbs,
# including missing completion times

dta_dir %>% 
  group_by(year_creation, month_creation) %>% 
  count()

# % suburb missing

dta_dir %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta_dir %>% 
               filter(is.na(official_suburb)) %>% 
               group_by(year_creation, month_creation) %>% 
               count(name = "total_missing")) %>% 
  mutate(percentage_missing_suburb = round(total_missing/total_ym*100, 2)) %>% 
  kable(format = "simple") %>%
  kable_styling( position = "left")

# exclude missing suburb

dta_dir <- dta_dir %>% 
  filter(!is.na(official_suburb))

# nr over time, per suburb, missing suburbs excluded now

tmp <- dta_dir %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta_dir %>% 
               group_by(year_creation, 
                        month_creation, official_suburb) %>% 
  count(name = "total_suburb")) %>% 
  mutate(percentage_suburb = total_suburb/total_ym*100) %>% 
  arrange(year_creation, month_creation,
          desc(percentage_suburb))

grid <- expand_grid(yr = unique(tmp$year_creation),
                    mnth = unique(tmp$month_creation))

tmp <- map2(grid$yr, grid$mnth,
     ~tmp %>% 
       filter(year_creation == .x & month_creation == .y) %>% 
       arrange(desc(percentage_suburb)) %>% 
       slice(1:5)) %>% 
  bind_rows()

tmp %>% 
  ggplot(aes(percentage_suburb, reorder(official_suburb, percentage_suburb), fill = month_creation))+
  geom_col()+
  facet_wrap(~year_creation + month_creation,
             scales = "free_y")

# department, branch, section, code_group not helpful
# dta_dir %>% 
#   group_by(code, cause_code) %>% 
#   count() %>% 
#   print(n = Inf)

# many cause codes NA, use code var only

x <- nrow(dta_dir)

tmp <- dta_dir %>% 
  group_by(official_suburb) %>% 
  count(name = "total_suburb") %>% 
  mutate(percentage_suburb = total_suburb/x*100) %>% 
  arrange(desc(percentage_suburb)) %>% 
  ungroup() %>% 
  slice(1:20)

tmp %>% 
  kable(format = "simple") %>%
  kable_styling( position = "left")

#

tmp <- dta_dir %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_month") %>% 
  inner_join(dta_dir %>% 
  group_by(year_creation, month_creation, official_suburb) %>% 
  count(name = "total_suburb")) %>% 
  ungroup() %>% 
    mutate(percentage = total_suburb/total_month*100) %>% 
    arrange(year_creation, month_creation, desc(percentage)) %>% 
  select(year_creation, month_creation, official_suburb,
         percentage) %>% 
    pivot_wider(names_from = month_creation, values_from = percentage) %>%  # add median across months
inner_join(dta_dir %>% 
             group_by(month_creation) %>% 
             count(name = "total_month") %>% 
             inner_join(dta_dir %>% 
  group_by(month_creation, official_suburb) %>% 
  count()) %>% 
  ungroup() %>% 
    mutate(percentage_suburb = n/total_month*100) %>% 
    group_by(official_suburb) %>% 
  summarise(med_percentage = median(percentage_suburb)) %>% 
  ungroup()) %>% 
  inner_join(tmp %>% 
               select(official_suburb)) %>% 
  arrange(desc(med_percentage))

tmp %>% 
  kable(format = "simple") %>%
  kable_styling( position = "left")

# explore codes for top 5

x <- tmp$official_suburb[1:5]

dta_dir %>% 
  filter(official_suburb %in% x) %>% 
  group_by(official_suburb, code) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(aes(n, code, fill = official_suburb))+
  geom_col(position = "dodge")

# top 3

select_suburbs <- c("PARKLANDS", "MILNERTON")

@@

@@

dta_dir <- dta_dir %>% 
  filter(!is.na(completion_timestamp))

@@

# summary(dta_dir$time_hours)

# check for outliers in time_hours

# tmp <- dta_dir %>%
#   summarise(q25 = quantile(time_hours, probs = 0.25),
#             q75 = quantile(time_hours, probs = 0.75),
#             iqr = q75 - q25,
#             ol_cutoff = 1.5*iqr + q75)
# 
# dta_dir %>% 
#   group_by(time_hours > tmp$ol_cutoff) %>% 
#   count()
# 
# dta_dir %>% 
#   filter(time_days >= tmp$ol_cutoff) %>% 
#   ggplot(aes(time_hours, official_suburb, 
#              colour = official_suburb))+
#   geom_jitter()+
#   facet_wrap(~code, scales = "free_y")+
#   theme(legend.position = "none")

#  create table with medians, q80 for all suburbs and for all of city

time_tables_make <- function(dataset = dta_dir, time_cutoff = NULL){

@@

  tabledta <- dataset %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
                 mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup())

@@

  dataset_x <- dataset %>% 
    filter(time_hours < time_cutoff)

  tabledta_below <- dataset_x %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup())

  dataset_x <- dataset %>% 
    filter(time_hours >= time_cutoff)

  tabledta_above <- dataset_x %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
  mutate(official_suburb = sub_txt) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup()) %>% 
  mutate(code = code_txt) %>% 
    bind_rows(dataset_x %>% 
                group_by(code) %>% 
                summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
              mutate(official_suburb = sub_txt)) %>% 
  bind_rows(dataset_x %>% 
  group_by(official_suburb, code) %>% 
  summarise(n = n(),
            med_time_hours = median(time_hours),
            q80_time_hours = quantile(time_hours, probs = 0.8)) %>% 
    ungroup())

@@

time_dta_list$all_times <- time_tables_make(dataset = dta_dir, time_cutoff = NULL)

# for all of city, all codes, split by times < or > 24hrs
tmp <- time_tables_make(dataset = dta_dir, time_cutoff = 24)

time_dta_list$below_24 <- tmp$tabledta_below 
time_dta_list$above_eq_24 <- tmp$tabledta_above

@@

time_dta_list$all_times %>% 
  filter(official_suburb == sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  kable(format = "simple", caption = "City-wide, all codes combined") %>%
  kable_styling( position = "left")

# filter by < 24 hrs

time_dta_list$below_24 %>% 
  filter(official_suburb == sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  kable(format = "simple", caption = "City-wide, all codes combined, only requests completed in less than 24 hours") %>%
  kable_styling( position = "left")

# > 24 hrs

time_dta_list$above_eq_24 %>% 
  filter(official_suburb == sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  kable(format = "simple", caption = "City-wide, all codes combined, only requests completed in 24 hours or more") %>%
  kable_styling( position = "left")

# split by 24 hours

x <- time_dta_list$below_24 %>% 
  filter(official_suburb == "ALL COMBINED" &
           code == "All codes combined") %>% 
  pull(n)

x <- time_dta_list$all_times %>% 
  filter(official_suburb == "ALL COMBINED" &
           code == "All codes combined") %>% 
  mutate(perc = x/n*100) %>% 
  pull(perc)

# x

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hours)) %>% 
  slice(1:5) %>% 
  kable(format = "simple", caption = "Top 5 suburbs with longest median completion times, all codes combined") %>%
  kable_styling( position = "left")

time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == code_txt &
           n >= n_cutoff) %>% 
  arrange(med_time_hours) %>% 
  slice(1:5) %>% 
  kable(format = "simple", caption = "Top 5 suburbs with shortest median completion times, all codes combined") %>%
  kable_styling(position = "left")

@@

# get codes for which > 5 requests for some suburbs

x <- dta_dir %>% 
  group_by(code, official_suburb) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  filter(n >= n_cutoff) %>% 
  ungroup() %>% 
  distinct(code) %>% 
  pull(code)

sub_txt <- "ALL COMBINED"
time_cutoff <- 24

p1 <- map(x,
    ~time_dta_list$below_24 %>% 
  filter(official_suburb != sub_txt &
           code == .x &
           n >= n_cutoff) %>% 
  select(official_suburb, code) %>% 
    distinct() %>% 
    inner_join(dta_dir %>% 
                 filter(time_hours < time_cutoff))) %>% 
  bind_rows() %>% 
  ggplot(aes(time_hours, official_suburb))+
    ggdist::stat_interval()+
  facet_wrap(~code, scales = "free_y", ncol = 1)

p2 <- map(x,
    ~time_dta_list$above_eq_24 %>% 
  filter(official_suburb != sub_txt &
           code == .x &
           n >= n_cutoff) %>% 
  select(official_suburb, code) %>% 
    distinct() %>% 
    inner_join(dta_dir %>% 
                 filter(time_hours >= time_cutoff))) %>% 
  bind_rows() %>% 
  ggplot(aes(time_hours, official_suburb))+
    ggdist::stat_interval()+
  facet_wrap(~code, scales = "free_y",
             ncol = 1)

ggpubr::ggarrange(p1, p2, ncol = 1, nrow = 2,
                  heights = c(2,1))

tmp <- map(x,
           ~time_dta_list$all_times %>% 
  filter(official_suburb != sub_txt &
           code == .x &
           n >= n_cutoff) %>% 
  arrange(desc(med_time_hours)))

x <- seq(1,length(tmp), by = 2)

kable(tmp[1:2], format = "simple") %>%
    kable_styling( position = "left")

@@
